pirouette: Determining the error BEAST2 makes in inferring a phylogeny

### 2019-03-07 article.tex
Describe twinning better

An optional step is to generate a 'twin tree' 
(Fig.~\ref{fig:pipeline}, 1a $\rightarrow$ 1b),
that will be analyzed in the same way as the true tree.
The twin tree has the same topology as the given phylogeny, 
yet its branching times are simulated according to 
a birth-death tree model.
The goal of this procedure is to generate a tree
accordingly to the tree prior used in the generative model, 
that is used as a control for the main experiment.
To produce such a birth-death tree, we maximize a birth-death likelihood [\cite{nee1994reconstructed}], conditioned on having the same number of tips as the original tree, to infer its parameters.
We use these parameters, which are the per-species speciation and extinction rates, to simulate the branching times for the twin tree, which we combine with the original tree's topology.

>>>>

An optional step is to generate a 'twin tree' 
(Fig.~\ref{fig:pipeline}, 1a $\rightarrow$ 1b),
that will be analyzed in the same way as the true tree.
The twin tree will be the true tree 
converted to follow the tree prior of the generative model. 
We do so, by finding the parameters 
(e.g. speciation and extinction rate for a birth-death model) 
with the maximum likelihood, 
conditioned on having the same number of tips as the original tree.
We use these parameters to simulate the branching times of the twin tree, 
which we combine with the original tree's topology.

Using a twin tree serves as a control: both the given/true tree
and twin tree will produce an error distribution.
For the true tree, this error distribution is caused by
the shape of the phylogeny (which is different from the tree priors used), 
the stochastic alignment simulation and stochastic Bayesian inference.  
The twin tree is created from the given phylogeny,
as it has the same topology, 
yet its branching times are simulated according to 
the (implemented) generative tree prior.
Due to this, this error distribution for the twin tree is caused 
only by the stochastic alignment simulation and stochastic Bayesian inference.
The difference between these two error distribution is the error caused
by the new/unimplemented tree prior.
